---
title: "Unit 7 Computer Vision mit RVision"
output: html_notebook
---

# Vorbereitungen
## Clear workspace
Löschen Sie die alte Umgebung, um in einem "neuen" R zu starten.
```{r}
rm(list=ls())
```
# Rvision
## Installation
### Devtools
Zur Installation der Rvision Library wird Devtools benötigt.

```{r}
#if (!require(devtools))
#  install.packages("devtools")
```


### ROpenCVLite
Im Anschluss muss ROpenCVLite installiert werden.
```{r}
#install.packages("ROpenCVLite")
```
```{r}
#library(ROpenCVLite)
```

```{r}
#devtools::install_github("swarm-lab/Rvision")
library(Rvision)
```

```{r}
# Find the path to the balloon1.png image provided with Rvision
path_to_image <- system.file("sample_img", "balloon1.png", package = "Rvision")

# Load the image in memory
my_image <- image(filename = path_to_image)
```



```{r}
plot(my_image)
```



# 3.	Rvision als Computer Vision Bibliothek für R
## Installation
### Devtools
Zur Installation der Rvision Library wird Devtools benötigt.

```{r}
#if (!require(devtools))
#  install.packages("devtools")
```


### ROpenCVLite
Im Anschluss muss ROpenCVLite installiert werden.
```{r}
#install.packages("ROpenCVLite")
```
```{r}
#library(ROpenCVLite)
```

```{r}
#devtools::install_github("swarm-lab/Rvision")
library(Rvision)
```

```{r}
# Find the path to the balloon1.png image provided with Rvision
path_to_image <- system.file("sample_img", "balloon1.png", package = "Rvision")

# Load the image in memory
my_image <- image(filename = path_to_image)
```



```{r}
plot(my_image)
```


## Input/output operations
### Image object from image file
```{r}
my_file_img <- image(system.file("sample_img", "bunny.png", package = "Rvision"))
```

### Write Image file
```{r}
write.Image(my_file_img, paste0(tempdir(), "/bunny.png"))
```

### Access image properties
```{r}
isImage(my_file_img)
dim(my_file_img)
nrow(my_file_img)
ncol(my_file_img)
bitdepth(my_file_img)
colorspace(my_file_img)
```

### Display image
```{r}
plot(my_file_img)
```

### Advanced operations on images
#### Convert color image to grayscale
```{r}
my_file_img_gray <- changeColorSpace(my_file_img, "GRAY")
plot(my_file_img_gray)
```

#### Split color image into separate channels
```{r}
my_channels <- split(my_file_img) # Order of channels is Blue, Green, Red, Alpha

layout(matrix(1:4, 2, 2, byrow = TRUE))
invisible(lapply(my_channels, plot))  # 'invisible' is used to hide the console output. It is not necessary otherwise.
```


#### Merge separate channels into color image
```{r}
my_merged_channels <- merge(my_channels)
plot(my_merged_channels)
```

#### Filter: Blurs 
Image von https://pixabay.com/de/photos/ara-papagei-vogel-hybrid-rot-grün-943228/
```{r}
img <- image("macaw-943228_1280.jpg")
boxFilter(img, k_height = 25, k_width = 25) %>% plot()
gaussianBlur(img, k_height = 25, k_width = 25, sigma_x = 5, sigma_y = 5) %>% plot()
medianBlur(img, k_size = 25) %>% plot()
sqrBoxFilter(img, k_height = 25, k_width = 25) %>% plot()
```

And apply edge detection algorithms such as sobel and laplacian.

```{r}
sobel(img) %>% plot()
```

Draws
```{r}
img1 <- cloneImage(img)
drawCircle(img1, x = 750, y = 750, radius = 200, color = "blue", 
           thickness = 10)
plot(img1)
```

Blob detection
By now we looked at a bunch of different functions but all of them have been used separately. Now let’s combine them to detect something inside the picture.

Bild von https://emilhvitfeldt.com/post/2018-02-14-rvision-a-first-look/
```{r}
img <- image("mundms.jpg")
plot(img)
```

```{r}
blob_fun <- function(img, fun, color = character()) {
  img %>%
    split() %>%
    do.call(fun, .) %>%
    medianBlur(15) %>%
    simpleBlobDetector(max_area = Inf, min_area = 10, blob_color = 255,
                       filter_by_convexity = FALSE, 
                       filter_by_inertia = FALSE, min_threshold = 0) %>%
    mutate(color = color)
} 

multi_draw <- function(img, blobs) {
  if (nrow(blobs) > 0) {
    for (i in 1:nrow(blobs)) {
      drawRectangle(img, 
                    blobs$x[i] - 1 + blobs$size[i], 
                    blobs$y[i] - 1 + blobs$size[i],
                    blobs$x[i] - 1 - blobs$size[i], 
                    blobs$y[i] - 1 - blobs$size[i], 
                    thickness = 5, color = blobs$color[1])
    }
  }
}
```

```{r}
blue <-   function(B, G, R) B > 150 & R < 200 & G < 200
red <-    function(B, G, R) R > 150 & B < 200 & G < 150
green <-  function(B, G, R) G > 150 & B < 200 & R < 200
yellow <- function(B, G, R) G > 150 & B < 200 & B > 150 & R > 150
orange <- function(B, G, R) G > 150 & B < 150 & R > 150
```


```{r}
blue_mms <-   blob_fun(my_img, blue, "blue")
red_mms <-    blob_fun(my_img, red, "red")
green_mms <-  blob_fun(my_img, green, "green")
yellow_mms <- blob_fun(my_img, yellow, "yellow")
orange_mms <- blob_fun(my_img, orange, "orange")

multi_draw(my_img, blue_mms)
multi_draw(my_img, red_mms)
multi_draw(my_img, green_mms)
multi_draw(my_img, yellow_mms)
multi_draw(my_img, orange_mms)

plot(my_img)
```

